---
title: "demoShiny"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
vignette: > 
  %\VignetteIndexEntry{demoShiny} 
  %\VignetteEngine{knitr::rmarkdown} 
  \usepackage[utf8]{inputenc} 
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The aim of the package `demoShiny` is to mimic the `demo` functionality for Shiny apps for a package.

# Which Shiny apps are available?

With `demoShiny` you can get an overview about all apps from the loaded packages:

```{r}
library("demoShiny")
demoShiny()
```

The output is a data frame with `package::topic` and the file or directory which would be called by `demoShiny`.

You can question for a specific apps

```{r}
demoShiny('demoShiny')
```

which delivers all demo apps of the package `demoShiny` **AND** all apps named `demoShiny`!

# How to run a single example app?

In case that for your topic is just one app available then no list will be returned but the Shiny demo app will be started:

```{r eval=FALSE}
# full topic
demoShiny('demoShiny::app1')
# if only one app1 is available then it will be run
demoShiny('app1')
# abbreviation for topics or packages can used
demoShiny('d::app1')
```

# App installation for a package in `inst/shiny`

If you develop a package then create under `inst` a directory `shiny`. 
Each subdirectory of `shiny` can contain one app. The name of the subdirectory is the topic name.

```{r}
list.files(system.file('shiny', package="demoShiny"), include.dirs=TRUE)
``` 

As you can see the `shiny` subdirectory of `demoShiny` contains several directories, e.g. `app1`, `silhouette`, and also a file `app1.R`. 

If you put a R file with the same name as a directory then the R file is sourced rather 
the app in the directory is called. The aim is to allow for a specfic calls to the app, e.g. by setting URL parameters:

```{r, code=readLines(system.file('shiny', 'app1.R', package='demoShiny')), eval=FALSE}
```